\Huge Conferences and Cost of Carbon

### 2019-06-03 main.tex
Final CP after call

A short-term response to both questions: ACM can choose to voluntarily impose
a price on its emissions using carbon offsets. 
\begin{itemize}
\item (What they are.)
\item giving ourselves a ``price signal''
is an effective way to begin raising awareness and changing organizational
behavior.
\item Lots of organizations (universities, companies) are doing this; some
ACM conferences are starting to experiment with voluntary carbon offset fees
at registration time. 
\item There are also some significant
concerns.
\item Concern:
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item Concern: It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\item This issue leads many people to argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\end{itemize}

Whether we choose to impose carbon offsets on ourselves or wait for
governments to do it, we need to begin gathering and analyzing data, to
better understand the 
carbon footprint of our conferences and the likely effects (both
environmental and scientific) of potential changes in the way they are
organized.  \bcp{Put in the most interesting discussion and perhaps show an
  interesting diagram.}
\bcp{Add some meat to that.
  \begin{itemize}
  \item List a few things we can do (and whose likely effects we'd need data
  to estimate)
  \begin{itemize}
  \item journalize conferences
  \item go virtual
  \item potential parts of a solution: regional conferences, virtual PC
  meetings, virtual participation, mega-conferences
  \end{itemize}
  \item cite our report
  \end{itemize}
}

@@

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make
  \item an excuse for citing the Climate Committee report and perhaps
  mentioning other SIGPLAN activities
  \item Decide what figures we want, if any
  \item go through all the suggestions below and in the referee reports,
  once more
  \item Think about adding headings, per Bishop's recommendation
  \item Go through all the comments and ideas below (including the CACM
  reviews) one last time
  \item Find a place for this: {\tt acm-climate} mailing list~\cite{acm-climate}
  \item Write a cover letter
  \begin{itemize}
  \item We tried hard to remove all incrementalism and make it much more
  hard hitting
  \item However, we did keep the suggestion of carbon offsets, hopefully
  in a more convincing / palatable / better argued form
  \item what else?
  \end{itemize}
  \end{itemize}
}

>>>>

One possible short-term response to both questions: ACM can choose to
voluntarily impose a price on its emissions using carbon offsets.
\begin{itemize}
\item (What they are.)
\item giving ourselves a ``price signal''
is an effective way to begin raising awareness and changing organizational
behavior.
\item Lots of organizations (universities, companies) are doing this; some
ACM conferences are starting to experiment with voluntary carbon offset fees
at registration time. 
\item There are also some significant
concerns.
\item Concern:
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item Concern: It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\item This issue leads many people to argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\end{itemize}

Whether we choose to impose carbon offsets on ourselves or wait for
governments to do it, there are also many things we can do to begin reducing
our footprint.  
\bcp{
  \begin{itemize}
  \item Briefly list a few things we can do (and whose likely effects we'd need data
  to estimate)
  \begin{itemize}
  \item journalize conferences
  \item go virtual
  \item potential parts of a solution: regional conferences, virtual PC
  meetings, virtual participation, mega-conferences
  \end{itemize}
  \item cite our report
  \end{itemize}
}
However, we urgently need to begin gathering and analyzing data, to
better understand the positive and negative effects of any of these
proposals.   
\bcp{Put the discussion of Figure 1 (and an accompanying figure
showing distance traveled to several instances of the same conference) here;
this illustrates the difficulty and the need for careful data gathering and
analysis.} 
All parts of ACM should be doing this kind of analysis.  (The acm-climate
mailing list is one place to exchange ideas about this.)

@@

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make (and the carbon-offsets-bad paper
  mentioned by the reviewer)
  \item Go through all the comments and ideas below (including the CACM
  reviews) one last time
  \item Find a place for this: {\tt acm-climate} mailing list~\cite{acm-climate}
  \item Think about adding headings, per Bishop's recommendation

  \item Write a cover letter
  \begin{itemize}
  \item We tried hard to remove all incrementalism and make it much more
  hard hitting
  \item However, we did keep the suggestion of carbon offsets, hopefully
  in a more convincing / palatable / better argued form
  \item what else?
  \end{itemize}
  \end{itemize}
}
